### 2009-02-24 doc/ws-programming-tutorial/doc/tex_echoservice/echoservice.tex
Started outline for the TLS echo service

The next service which will be presented is the echo service. It simply returns the received message back to the client.
Depending on the operation requested by the client, the letters of the message will be reordered reverse or not.
The goal of this chapter is to offer a deeper knowledge in message processing. Furthermore the \textit{WSDL} (Web Services Description Language) shall be introduced along with this example.

@@

Web Services are often reachable for a large set of users in order to easily access complex information. In many cases the Web Service are capable to replace HTML pages i.e. access to databases like Pubmed or the NLM catalog.
% http://www.ncbi.nlm.nih.gov/entrez/query/static/esoap_help.html
In contrary to HTML the interfaces of the data are well defined and easier to find for machines. bla...
Due to that reason, the way to access the web service has to be defined in an own language: \textit{WSDL} (Web Services Description Language).
WSDL is a meta language which determines the structure of the messages along with its permitted elements, the accepted operations, the supported protocols and the address to reach the service. 
The WSDL for the echo service which shall be implemented in this chapter is to be seen in Listing~\ref{lst:echo_wsdl}. There are five main elements to describe a service:
\begin{itemize}
	\item \textbf{Types} --- Definition of the data types used by the messages, line~\ref{lst_code:echo_wsdl_types}.
	\item \textbf{Message} --- Assignments which data types are representing a message, line~\ref{lst_code:echo_wsdl_message1} and \ref{lst_code:echo_wsdl_message2}.
	\item \textbf{Port type} --- \parbox[t]{13cm}{Assignment of the interface: One-way (input), request-response (input, output), solicit-response (input, output, fault), notification (output). The request-response interface is used in line~\ref{lst_code:echo_wsdl_portType}.}
	\item \textbf{Binding} --- Defines the concret protocol and data format used for the message transmission, line~\ref{lst_code:echo_wsdl_binding}.
	\item \textbf{Service} --- Specifies the address to bind a service, line~\ref{lst_code:echo_wsdl_service}.
\end{itemize}
%\textcolor{white}{newline}
\lstsetJUSTXML
\lstinputlisting
	[
	label=lst:echo_wsdl,
	caption={[WSDL file describing the echo service. Filename: echo.wsdl]
	\textbf{HWSDL file describing the echo service. Filename: echo.wsdl}}
	]
{../src/services/echoservice/echo.wsdl}

@@

%    * Quality-of-Service-Informationen
%    * Taxonomien/Ontologien zur semantischen Einordnung des Services

@@

The service defined by the WSDL file in the previous section shall now be implemented. The source code of the C++ file is shown in Listing~\ref{lst:echo_service_cpp}. Again the header file will be set aside for it contains to much redundant information.

\lstinputlisting
	[
	label=lst:echo_service_cpp,
	caption={[C++ implementation of the echo service. Filename: echoservice.cpp]
	\textbf{C++ implementation of the echo service. Filename: echoservice.cpp}}
	]
{../src/services/echoservice/echoservice.cpp}

>>>>

The next service to be presented is the echo service which returns the received message back to the client.
Furthermore the client has to choose between the operations ``ordinary'' or ``reverse''.
Depending on that operation the message will be returned directly or its letters will be reordered reverse. % without manipulation
The goal of this chapter is to offer a deeper knowledge about message processing. Furthermore the \textit{WSDL} (Web Services Description Language) shall be introduced along with this example.

@@

Web Services are often reachable for a large set of users in order to easily access complex information. In many cases the Web Service are capable to replace HTML pages i.e. to access to databases like Pubmed or the NLM catalog.
% http://www.ncbi.nlm.nih.gov/entrez/query/static/esoap_help.html
In contrary to HTML which describes a human readable document the interfaces of Web Services are well defined and easier to interpret for machines.
In general the client is not familiar with the functionality of the service.
Due to that reason, the access to a web service can be defined in a \textit{WSDL} (Web Services Description Language) file.
WSDL is a meta language which describes the structure of the messages, the intended use of the message, the supported protocols and the endpoint of the service (URL).
The WSDL file which specifies the echo service of this chapter is to be seen in Listing~\ref{lst:echo_wsdl}. 
It consisits of five main WSDL elements:
\newcommand{\parboxWidth}{13cm}
\begin{itemize}
	\item \textbf{Types} --- The element \textit{types} contains the description of the message structures which is written in the language XSD (XML Schema Definition). The applicable data types of the echo service are defined in  line~\ref{lst_code:echo_wsdl_types}.

	\item \textbf{Message} --- Within the element \textit{message} a subset of the previously defined types are assigned to be a message. In case of the echo service two messages are designated: echoRequest and echo Response, see lines line~\ref{lst_code:echo_wsdl_message1} and \ref{lst_code:echo_wsdl_message2}.

	\item \textbf{Port type} --- The element \textit{portType} is used to assign the messages to an interface. Four interface types can be distinguished: One-way (input), request-response (input, output), solicit-response (input, output, fault) and notification (output).
	The echo service realises a simple request-response interface which is declared subsequent line~\ref{lst_code:echo_wsdl_portType}. % in the lines followed by the line X

	\item \textbf{Binding} --- The protocol and the data format used for the message transmission are denoted in the element \textit{binding}. Possible style attributes are \textit{document} or \textit{rpc} (Remote Procedure Call). The transport attribute defines the protocol which is regularly HTTP. For each operation a corresponding SOAP action has to be defined. Additionally the input and output has to be specified to be either \textit{literal} or \textit{encoded}~\cite{BUTEK_2009}. The service implemented in this chapter will use the binding \textit{document}/\textit{literal} and the protocol HTTP which is to be seen in line~\ref{lst_code:echo_wsdl_binding}.

% The style attribute can be "rpc" or "document". In this case we use document. The transport attribute defines the SOAP protocol to use. In this case we use HTTP.
%The operation element defines each operation that the port exposes.
%For each operation the corresponding SOAP action has to be defined. You must also specify how the input and output are encoded. In this case we use "literal".
%  http://www.ibm.com/developerworks/webservices/library/ws-whichwsdl/
%   1. RPC/encoded    (Remote Procedure Call)
%   2. RPC/literal
%   3. Document/encoded
%   4. Document/literal
% The terminology here is very unfortunate: RPC versus document. These terms imply that the RPC style should be used for RPC programming models and that the document style should be used for document or messaging programming models. That is not the case at all. The style has nothing to do with a programming model. It merely dictates how to translate a WSDL binding to a SOAP message. Nothing more. You can use either style with any programming model.
%
% RPC/literal SOAP message for myMethod
%
%<soap:envelope>
%    <soap:body>
%        <myMethod>
%            <x>5</x>
%            <y>5.0</y>
%        </myMethod>
%    </soap:body>
%</soap:envelope>
%
%  RPC/encoded SOAP message for myMethod
% 
% <soap:envelope>
%     <soap:body>
%         <myMethod>
%             <x xsi:type="xsd:int">5</x>
%             <y xsi:type="xsd:float">5.0</y>
%         </myMethod>
%     </soap:body>
% </soap:envelope>

	\item \textbf{Service} --- Within the last WSDL element the endpoint of the service is specified. As to be seen in line~\ref{lst_code:echo_wsdl_service} the endpoint of the echo service is assigned to \textit{http://localhost:60000/echo}.

\end{itemize}
%\textcolor{white}{newline}
\lstsetJUSTXML
\lstinputlisting
	[
	label=lst:echo_wsdl,float=p,
	caption={[WSDL file describing the echo service. Filename: echo.wsdl]
	\textbf{WSDL file describing the echo service. Filename: echo.wsdl}}
	]
{../src/services/echoservice/echo.wsdl}

@@

%    * Quality-of-Service-Informationen
%    * Taxonomien/Ontologien zur semantischen Einordnung des Services
\clearpage

@@

The implementation of the service defined in the WSDL file of the previous section will blub. The source code of the C++ file is shown in Listing~\ref{lst:echo_service_cpp}. Again the header file will be set aside for it contains to much redundant information.

\lstsetCPP
\lstinputlisting
	[
	label=lst:echo_service_cpp,
	caption={[C++ implementation of the echo service. Filename: echoservice.cpp]
	\textbf{C++ implementation of the echo service. Filename: echoservice.cpp}}
	]
{../src/services/echoservice/echoservice.cpp}

### 2009-02-24 doc/ws-programming-tutorial/doc/tex_pesistentservice/peristentservice.tex
Started outline for the TLS echo service

>>>>

if bartender_url.startswith('https'):
    key_file = os.environ.get('ARC_KEY_FILE', None)
    cert_file = os.environ.get('ARC_CERT_FILE', None)
    proxy_file = os.environ.get('ARC_PROXY_FILE', None)
    ca_file = os.environ.get('ARC_CA_FILE', None)
    ca_dir = os.environ.get('ARC_CA_DIR', None)

export ARC_KEY_FILE=/local/glodek/clientKey.pem
export ARC_CA_FILE=/local/glodek/clientCA.pem
export ARC_CERT_FILE=/local/glodek/clientCert.pem

does the daemon runs the service single threaded

race conditions
\begin{itemize}
 \item Transaktionen
 \item nur lesen
 \item jeder prozess schreibt in seine eigene Datei
 \item Gibt es einen     // andere Zugriffe abblocken
    flock (\$fp, LOCK\_EX);  (atomare befehle)
 	wie bei php??
 \item Peterson Algorithmus
 \item Was passiert beim Ausfall (Time out - Transaktion zurück nehmen)
\end{itemize}

\section{Schlusswort}

Other tutorials are:\\
\\
%Oxana reported the status of OGF tutorials:
\begin{itemize}
 \item first tutorial will be given by Oxana and will deal with how to add the 
resources to Nordugrid, .... (will be related mostly to production ARC)
 \item second tutorial will be given by Gabor and he will show the 
interoperability of ARC (video demo will be shown). A-REX - Unicore 
interoperability.
 \item there will be also a tutorial related to ETICS system where the 
possibility of ETICS system to submit a job to ARC and Unicore will be 
presented. The ETICS team has not contacted so far.
\end{itemize}

### 2009-02-24 doc/ws-programming-tutorial/doc/tex_tls_echoservice/tls_echoservice.tex
Started outline for the TLS echo service

TLS provides security and data integrity

Diffrent kind of security is intended;
\begin{enumerate}
 \item Integrity (data is not manipulated along the transmission)
 \item Confidentiality 
 \item Authenticity (Server and client sided)
 \item Authorization (Server and client sided)
\end{enumerate}

The first two goals can be reached by encrypting the channel/connection between client and server. An approach 
%sich bewähren / behaupten
which stand the test of time is to introduce a TLS (Transport Layer Security) also known as SSL (Secure Sockets Layer).
Authenticity, Confidentiality, Integrity
The client wants to reassure himself to send his vulnerable data only to the server who can prove its correct identity.
Furthermore a prove of authenticity is needed. % Sich versichern, dass das Gegenüber der ist, für welchen er sich ausgibt
It .... does fancy stuff ...
%
%
Authorization:  The server on the other side takes an interest in limitate its ressources to a close circle of users. Above all no foreign clients shall be able to use the services.\\

clientCA   - Authority guarantee for identity
clientCERT - Certificate given
clientKEY  - Secret key of the client to read messages, encrypted by the public key in the certificate!

@@

@@

\lstsetCPP
\lstinputlisting
	[
	label=lst:arcecho_arched_xml,
	caption={[HED configuration file for the Arc intern echo service. Filename: arcecho\_no\_ssl.xml]
	\textbf{HED configuration file for the Arc intern echo service. Filename: arcecho\_no\_ssl.xml\textcolor{white}{hmf}}}
	]
{../src/clients/tlsechoclient/tlsechoclient.cpp}

\lstsetCPP

\lstinputlisting
	[
	label=lst:arcecho_arched_xml,
	caption={[HED configuration file for the Arc intern echo service. Filename: arcecho\_no\_ssl.xml]
	\textbf{HED configuration file for the Arc intern echo service. Filename: arcecho\_no\_ssl.xml\textcolor{white}{hmf}}}
	]
{../src/services/tlsechoservice/tlsechoservice.cpp}

\lstsetARCHEDXML
\begin{minipage}[t]{\textwidth}
\lstinputlisting
	[
	label=lst:arcecho_arched_xml,
	caption={[HED configuration file for the Arc intern echo service. Filename: arcecho\_no\_ssl.xml]
	\textbf{HED configuration file for the Arc intern echo service. Filename: arcecho\_no\_ssl.xml\textcolor{white}{hmf}}}
	]
{../src/services/tlsechoservice/arched_tls_echoservice.xml}
\end{minipage}

\lstsetKSH
\begin{minipage}[t]{\textwidth}
\begin{lstlisting}[
label=lst:invokation_arched_timeservice,
caption={[Transformation in eine uniforme konzentrische Verteilung.]
         \textbf{Transformation in eine uniforme konzentrische Verteilung.\textcolor{white}{hmf}}}]
$ rm -f /var/log/arched.log
$ arched -c arched_echoservice.xml  && echo jo ||echo n
$ tail -n100 -f /var/log/arched.log
$ killall arched
\end{lstlisting}
\end{minipage}

\lstsetKSH
\begin{minipage}[t]{\textwidth}
\begin{lstlisting}[
label=lst:invokation_arched_timeservice,
caption={[Transformation in eine uniforme konzentrische Verteilung.]
         \textbf{Transformation in eine uniforme konzentrische Verteilung.\textcolor{white}{hmf}}}]
$ ./echoclient
Tue Feb 17 17:04:08 2009
\end{lstlisting}
\end{minipage}

\lstsetJUSTXML
\begin{minipage}[t]{\textwidth}
\begin{lstlisting}[
label=lst:timeservice_cpp_source,
caption={[Transformation in eine uniforme konzentrische Verteilung.]
         \textbf{Transformation in eine uniforme konzentrische Verteilung.\textcolor{white}{hmf}}}]
<soap-env:Envelope xmlns:echo="urn:echo" xmlns:soap-enc="http://schemas.xmlsoap.org/soap/encoding/" xmlns:soap-env="http://schemas.xmlsoap.org/soap/envelope/" xmlns:xsd="http://www.w3.org/2001/XMLSchema" xmlns:xsi="http://www.w3.org/2001/XMLSchema-instance">
	<soap-env:Body>
		<echoRequest:echo>
			<echo:say>Der_Berg_ruft</echo:say>
		</echoRequest:echo>
	</soap-env:Body>
</soap-env:Envelope>
\end{lstlisting}
\end{minipage}

\lstsetJUSTXML
\begin{minipage}[t]{\textwidth}
\begin{lstlisting}[
label=lst:timeservice_cpp_source,
caption={[Transformation in eine uniforme konzentrische Verteilung.]
         \textbf{Transformation in eine uniforme konzentrische Verteilung.\textcolor{white}{hmf}}}]
<soap-env:Envelope xmlns:echo="urn:echo" xmlns:soap-enc="http://schemas.xmlsoap.org/soap/encoding/" xmlns:soap-env="http://schemas.xmlsoap.org/soap/envelope/" xmlns:xsd="http://www.w3.org/2001/XMLSchema" xmlns:xsi="http://www.w3.org/2001/XMLSchema-instance">
  <soap-env:Body>
    <echo:echoResponse>
      <echo:hear>[ Der_Berg_ruft ]</echo:hear>
    </echo:echoResponse>
  </soap-env:Body>
</soap-env:Envelope>
\end{lstlisting}
\end{minipage}

>>>>

The web service presented in the previous chapter has the mayor drawback that the communication between the two endpoints is unsecure.
Due to that reason the service  shall be extended by an additional layer called TLS (Transport Layer Security) to provide a certain degree of securtity on \task{Grid-level <-- explain that}.
%
In general the internet security is often subdivided into the following categories:~\cite{TANNENBAUM_2001}\task{verfiy citation}
\begin{itemize}
	\item \textbf{Confidentiality} --- Protection of the data against passiv attacks (such as publicise message content)

	\item \textbf{Authentication} --- Verification of the Authenticity  of the communications partner.

	\item \textbf{Integrity} --- Protection against interception and manipulation,replay,insertion, etc.  of a message.

	\item \textbf{Non-repudiation} --- Preventing the sender to repudiate the message transmitted by him.

	\item \textbf{Access control} --- Restrict the access to ressources.

	\item \textbf{Availability} --- Ensure a system is always usable which is challenged by several attacks.

\end{itemize}
%1-21   Gebräuchliche Dienste
%     Identifizierung           Vermerk
%     Berechtigung              Zugriff
%     Lizenz/Zertifizierung     Gültigkeitsprüfung
%     Unterschrift              Zeitpunkt des Auftretens
%     Bezeugung                 Abstimmung
%     Übereinstimmung           Eigentum
%     Zuverlässigkeit           Registrierung
%     Quittungen                Genehmigung/Verbot
%     Bestätigung des Ursprungs Privatsphäre
%
% Nach Sicherheit in verteilten Systemen, ITM Lübeck
The TLS to be introduced provides: Confidentiality, authentication, integrity, non-repudiation and access control.
It is introduced after the TCP layer. 
%
Before presenting the implementation of the new secure echo service the basic concept of a secure certifcate based connection shall be explained. Its not the goal to give an exact technical desciption but to give a first inside what is required to ensure the security of the layer.

% It is recommand to satifiy as much categories as possible. 
%authentication , confidentiality and integrity protection of TCP-based communication --- non-repudiation due to private key, access control to our service.

\section{Transport Layer Security}

The TLS is a protocol which provides a secure connection between two endpoints. It is located directly upon the TCP/IP layers and uses typically an asymmetric encryption to establish the connection (alternatively a symmetric pre-shared key may be used). After the communication has successfully established, both participants are switching to another encryption method which is based on a new negotiated symmetric key.
%    1. Peer negotiation for algorithm support
%    2. Key exchange and authentication
%    3. Symmetric cipher encryption and message authentication   - from wikipedia
%
%
Symmetric and asymmetric encryption are the two main classes of cryptography algorithms.
In case of a symmetric encryption both participants are holding the same secret key. 
Symmetric encryption can be ranked as being very secure but its downside is the key distribution which is very difficult in practice. 
Ideally the secret key is transmitted over a secure channel which is either a complete diffrent medium (i.e. a letter) or an channel encrypted with another secret key.
Asymmetric encryption follows a diffrent functional principle. While the symmetric encryption utilise one shared secret, the asymmetric ecryption is based on two keys: a private key and public key. As the names imply the private key is kept secret and never shared while the public key is available for everyone. Messages encrypted with the public key can only be decrypted with the private key and the other way round, messages encrypted with the private key can only be decrypted with the public key. The figure~\ref{fig:asymmetric_encryption} illustrates the circumstances of the case.\\
\begin{figure}[htb]
	\centering%epstopdf async.eps
	\subfloat[Texttext\label{fig:cgd}]
		{\includegraphics[width=12cm]{tex_tls_echoservice/async.pdf}}\\
	\subfloat[Texttext\label{fig:cgd}]
		{\includegraphics[width=12cm]{tex_tls_echoservice/async2.pdf}}
	\label{fig:asymmetric_encryption}
	\mycaption{specific}{general}
\end{figure}

At startup of the communication process A (Alice) who desires a secure connection transmits her public key to B (Bob).
Bob is now able to encrypt the messages such that only A is able to decrypt them.
That way confidentiality and integrity of messages are easily realised.
Non-repudiation, authentication and due to that access control are not given because the identity of Alice is not proven.
In order to be able to check identities so called certificates have been introduced.
Certificates render the possibility to check the identity of its owner. They are signed by a certificate authority (CA) which's identity can be resolved to another CA or is  pre-configured to be trusted.
A certificate is composed of its owner's public key, his identity, the name of the signing CA and a signiture which is a hash-value of the certificate encrypted with the private key of the CA. 
That way the CA confirms the identity of the certificate owner. 
To obtain a certificate a request has to be submitted to a CA which verifies the identity of the requesting person and signs it, if it comes to the result that the authenticity is valid. Figure~\ref{fig:certificate_request} shows the procedure to gain a certificate.
\begin{figure}[htb]
	\centering%epstopdf certificates.eps
 	\includegraphics[width=13cm]{tex_tls_echoservice/certificates.pdf}
	\mycaption{specific}{general}
	\label{fig:certificate_request}
\end{figure}
Figure~\ref{fig:verification_of_certificates} shows a usecase where Alice wants to resolve the identity of Bob. Alice submitts her request to Bob along with a challange consisting of a random number $n$. Bob encrypts the number with his private key and returns it together with his certificate. With the usage of the public key, Alice is able to decrypt the challange which implies that, if the certificate is to be trusted, the identity of Bob is to be trusted. Unfortunately Alice is unable to verify the certificate because it is signed by an unknown CA called CA 1. She establishes the connection to CA 1 in order to resolve the identity of that certificate authority. Again Alice sends a challenge --- this time to the certificate authority CA 1. CA 1 encrypts the challange with its private key and submits the result along with its certificate. Again Alice validates the certificate sucessfully. 
The certificate was signed by a CA called CA 2 which she is able to locate as a pre-configured certificate. Due to the reason she trusts CA 2, she can trust CA 1 and finally Bob.

\begin{figure}[htb]
	\centering%epstopdf verification.eps 
	\includegraphics[width=13cm]{tex_tls_echoservice/verification.pdf}
	\mycaption{specific}{general}
	\label{fig:verification_of_certificates}
\end{figure}

The advantages of certificates are
o easy scalable to a larger set of users
o VOMs are realisable
o Infrastructure is given and easily to maintain
o In general the pre-configured organistion take money to sign certifcates, but they can also be created locally.

TLS also supports the more secure bilateral connection mode (typically used in enterprise applications), in which both ends of the "conversation" can be ensured with whom they are communicating

o What do we need to get a service running
clientCA   - Authority guarantee for identity
clientCERT - Certificate given
clientKEY  - Secret key of the client to read messages, encrypted by the public key in the certificate!

@@

%The first two goals can be reached by encrypting the channel/connection between client and server. An approach 
%sich bewähren / behaupten
%which stand the test of time is to introduce a TLS (Transport Layer Security) also known as SSL (Secure Sockets Layer).
%Authenticity, Confidentiality, Integrity
%The client wants to reassure himself to send his vulnerable data only to the server who can prove its correct identity.
%Furthermore a prove of authenticity is needed. % Sich versichern, dass das Gegenüber der ist, für welchen er sich ausgibt
%It .... does fancy stuff ...
%
%
%Authorization:  The server on the other side takes an interest in limitate its ressources to a close circle of users. Above all no %foreign clients shall be able to use the services.\\

\clearpage
\section{Service}

@@

4 types:
                <KeyPath>./clientKey.pem</KeyPath>
                <CertificatePath>./clientCert.pem</CertificatePath>
                <CACertificatePath>./serviceCA.pem</CACertificatePath>

\lstsetCPP
\lstinputlisting
	[
	label=lst:tls_echo_service_cpp,
	caption={[HED configuration file for the Arc intern echo service. Filename: arcecho\_no\_ssl.xml]
	\textbf{HED configuration file for the Arc intern echo service. Filename: arcecho\_no\_ssl.xml\textcolor{white}{hmf}}}
	]
{../src/services/tlsechoservice/tlsechoservice.cpp}

\lstsetARCHEDXML
\lstinputlisting
	[
	label=lst:tls_echo_arched_xml,float=htb,
	caption={[HED configuration file for the Arc intern echo service. Filename: arcecho\_no\_ssl.xml]
	\textbf{HED configuration file for the Arc intern echo service. Filename: arcecho\_no\_ssl.xml\textcolor{white}{hmf}}}
	]
{../src/services/tlsechoservice/arched_tls_echoservice.xml}

\lstsetKSH
\begin{lstlisting}[
label=lst:tls_echo_arched_invoke,float=htb,
caption={[Transformation in eine uniforme konzentrische Verteilung.]
         \textbf{Transformation in eine uniforme konzentrische Verteilung.\textcolor{white}{hmf}}}]
$ rm -f /var/log/arched.log
$ arched -c arched_echoservice.xml  && echo jo ||echo n
$ tail -n100 -f /var/log/arched.log
$ killall arched
\end{lstlisting}

\clearpage
\section{Client}

\lstsetCPP
\lstinputlisting
	[
	label=lst:tls_echo_client_cpp,
	caption={[HED configuration file for the Arc intern echo service. Filename: arcecho\_no\_ssl.xml]
	\textbf{HED configuration file for the Arc intern echo service. Filename: arcecho\_no\_ssl.xml\textcolor{white}{hmf}}}
	]
{../src/clients/tlsechoclient/tlsechoclient.cpp}

\lstsetKSH
\begin{lstlisting}[
label=lst:tls_echo_client_invoke,float=htb,
caption={[Transformation in eine uniforme konzentrische Verteilung.]
         \textbf{Transformation in eine uniforme konzentrische Verteilung.\textcolor{white}{hmf}}}]
$ ./echoclient
Tue Feb 17 17:04:08 2009
\end{lstlisting}

\lstsetJUSTXML
\begin{lstlisting}[
label=lst:tls_echo_request_XML,float=htb,
caption={[Transformation in eine uniforme konzentrische Verteilung.]
         \textbf{Transformation in eine uniforme konzentrische Verteilung.\textcolor{white}{hmf}}}]
<soap-env:Envelope xmlns:tlsecho="urn:tlsecho" xmlns:soap-enc="http://schemas.xmlsoap.org/soap/encoding/" xmlns:soap-env="http://schemas.xmlsoap.org/soap/envelope/" xmlns:xsd="http://www.w3.org/2001/XMLSchema" xmlns:xsi="http://www.w3.org/2001/XMLSchema-instance">
  <soap-env:Body>
    <tlsecho:tlsechoRequest>
      <tlsecho:say operation="ordinary">text_to_be_transmitted</tlsecho:say>
    </tlsecho:tlsechoRequest>
  </soap-env:Body>
</soap-env:Envelope>
\end{lstlisting}

\lstsetJUSTXML
\begin{lstlisting}[
label=lst:tls_echo_response_XML,float=htb,
caption={[Transformation in eine uniforme konzentrische Verteilung.]
         \textbf{Transformation in eine uniforme konzentrische Verteilung.\textcolor{white}{hmf}}}]
<soap-env:Envelope xmlns:tlsecho="urn:tlsecho" xmlns:soap-enc="http://schemas.xmlsoap.org/soap/encoding/" xmlns:soap-env="http://schemas.xmlsoap.org/soap/envelope/" xmlns:xsd="http://www.w3.org/2001/XMLSchema" xmlns:xsi="http://www.w3.org/2001/XMLSchema-instance">
  <soap-env:Body>
    <tlsecho:tlsechoResponse>
      <tlsecho:hear>[ text_to_be_transmitted ]</tlsecho:hear>
    </tlsecho:tlsechoResponse>
  </soap-env:Body>
</soap-env:Envelope>
\end{lstlisting}
